Eye Fitting Straight Lines in the Modern Era (JCGS-22-045)

### 2022-07-19 analysis/you-draw-it-eyefitting-analysis.Rmd
updating analysis to incorporate deming regression instead.

---
title: "Eye Fitting Straight Lines in the Modern Era"
subtitle: "Data Analysis"
author: "Emily Robinson"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
library(knitr)
```

@@

+ Load libraries
+ Functions for computing confidence intervals

```{r setup2}
library(tidyverse)
library(kableExtra)
library(readr)
library(here)
library(mgcv)
library(lme4)
library(lmerTest)
library(emmeans)
source(here("analysis/gamm-predict-function.R"))
```

@@

De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).

```{r data}
eyefitting_model_data  <- read_csv(here("data/youdrawit-eyefitting-model-data.csv"))

factorCols <- c("participantID", "nick_name", "study_starttime", "age", "gender", "academic_study",
                "recruitment", "plotID", "parm_id")
eyefitting_model_data[,factorCols] <- lapply(eyefitting_model_data[,factorCols], factor)
```

```{r data-table, echo = F}
eyefitting_model_data[1:10,] %>%
  kbl() %>%
  kable_paper() %>%
  scroll_box(width = "100%", height = "200px")

eyefitting_model_data <- eyefitting_model_data %>%
  dplyr::mutate(`Parameter Choice` = parm_id)
```

@@

### OLS with loess smoother

```{r yloess-ols-plot}
eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = yloess, group = plotID), alpha = 0.5, color = "steelblue") +
  geom_line(alpha = 0.2, aes(y = yols, group = participantID)) +
  # geom_line(alpha = 0.2, aes(y = ypca, group = participantID), linetype = "dashed") +
  facet_wrap(~ parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  ggtitle("OLS")
```

### PCA with loess smoother

```{r yloess-pca-plot}
eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = yloess, group = plotID), alpha = 0.5, color = "steelblue") +
  # geom_line(alpha = 0.2, aes(y = yols, group = participantID)) +
  geom_line(alpha = 0.2, aes(y = ypca, group = participantID)) +
  facet_wrap(~ parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  ggtitle("PCA")
```

### Residuals with loess smoother

@@

```{r residual-plot}
eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = residualols.loess, group = plotID, color = "OLS"), alpha = 0.3) +
  geom_line(aes(y = residualpca.loess, group = plotID, color = "PCA"), alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  scale_color_manual("Estimate", values = c("steelblue", "orange"))
```

@@

```{r, anova-lmer, echo = F}
sv <- c("participantID", "parm_id", "x", "x:parm_id", "residual")
df <- c("(50 - 1) = 49", "(4 - 1) = 3", "1", "(4 - 1) = 3", "143 - by subtraction")
data.frame("SV" = sv, "DF" = df) %>% kable()
```

@@

```{r lmer, fig.height = 9}
# OLS
eyefitting.ols.lmer <- lmer(residualols ~ -1 + parm_id + x:parm_id + (1|participantID),
                       data = eyefitting_model_data)
anova(eyefitting.ols.lmer)

# PCA
eyefitting.pca.lmer <- lmer(residualpca ~ -1 + parm_id + x:parm_id + (1|participantID),
                            data = eyefitting_model_data)
anova(eyefitting.pca.lmer)

@@

# write.csv(eyefitting.preds.lmer, "results/youdrawit-eyefitting-lmerpred-data.csv", row.names = F, na = "")

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data, aes(x = x, y = residualols, group = plotID, color = "OLS"), alpha = 0.1) +
  geom_line(data = eyefitting_model_data, aes(x = x, y = residualpca, group = plotID, color = "PCA"), alpha = 0.1) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.7) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PCA"), color = NA, alpha = 0.7) +
  geom_line(aes(y = emmean.pca, color = "PCA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 2) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PCA"))

@@

```{r gamm, fig.height = 9}
# OLS
eyefitting.ols.gamm <- bam(residualols ~ parm_id + s(x, by = parm_id) + 
                             s(participantID, bs = "re") +
                             s(x,participantID, bs = "re"),
            method = "REML",
            data = eyefitting_model_data)

@@

# PCA
eyefitting.pca.gamm <- bam(residualpca ~ -1 + parm_id + s(x) +
                             s(x, by = parm_id) +
                             s(participantID, bs = "re") +
                             s(x,participantID, bs = "re"),
                           method = "REML",
                           data = eyefitting_model_data)
# evaluate gamm
plot(eyefitting.pca.gamm, pages = 1,all.terms=TRUE)

# Obtain Predictions
eyefitting.grid.gamm <- expand_grid(parm_id = c("S", "V", "F", "N"),
                                    x = seq(0,20, 0.5),
                                    participantID = eyefitting_model_data$participantID[1])

@@

# write.csv(eyefitting.grid.gamm, "results/youdrawit-eyefitting-gammpred-data.csv", row.names = F, na = "")

# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data, aes(x = x, y = residualols, group = plotID, color = "OLS"), alpha = 0.1) +
  geom_line(data = eyefitting_model_data, aes(x = x, y = residualpca, group = plotID, color = "PCA"), alpha = 0.1) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.5) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PCA"), color = NA, alpha = 0.5) +
  geom_line(aes(y = pca.pred, color = "PCA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 2) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) 
eyefitting.gamm.plot
```

>>>>

---
title: "Eye Fitting Straight Lines in the Modern Era (JCGS-22-045)"
subtitle: "Data Analysis"
author: "Emily A. Robinson, Reka Howard, and Susan VanderPlas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
```

@@

+ Load required libraries

```{r setup2}
# formatting of tables
library(knitr)
library(kableExtra)

# read in data
library(readr)

# data management, plotting, etc.
library(tidyverse)

# used to calculate demming regression equaiton
library(mcr)

# used to fit linear mixed model to residual trend
library(lme4)
library(emmeans)

# used to fit generalized additive mixed model to residual trend
library(mgcv)
```

+ Source code to load functions for computing confidence intervals

```{r setup3}
#' library(lme4)
#' library(mgcv)
#' lmer_model <- lmer(Reaction ~ Days + (Days || Subject), data = sleepstudy)
#' ga_model <- gam(Reaction ~ Days + s(Subject, bs = "re") + s(Days, Subject, bs = "re"),
#'   data = sleepstudy,
#'   method = "REML"
#' )
#'
#' head(
#'   data.frame(
#'     lmer = predict(lmer_model),
#'     gam = predict_gamm(ga_model)
#'   )
#' )
#'
#' head(
#'   cbind(
#'     lmer = predict(lmer_model, re.form = NA),
#'     gam1 = predict_gamm(ga_model, re_form = NA),
#'     gam2 = predict_gamm(ga_model,
#'       exclude = c("s(Subject)", "s(Days,Subject)")
#'     )
#'   )
#' )
#'
#' head(predict_gamm(ga_model, se = TRUE))
#' @export
predict_gamm <- function(
  model,
  newdata,
  re_form = NULL,
  se = FALSE,
  include = NULL,
  exclude = NULL,
  keep_prediction_data = FALSE,
  ...) {

  # Note because predict doesn't use NULL, can't use NULL for new_data arg or
  # even a differently named arg, and I'm not going into the weeds of rlang to
  # find a hack.

  # basic checks
  if (!inherits(model, "gam")) stop("Need a gam object.")

  if (!rlang::is_null(include) && !rlang::is_character(include)) {
    stop("include must be NULL or character.")
  }

  if (!rlang::is_null(exclude) && !rlang::is_character(exclude)) {
    stop("exclude must be NULL or character.")
  }

  if (!rlang::is_null(re_form) &&
      !rlang::is_na(re_form) &
      !rlang::is_character(re_form)) {
    stop("re_form must be NULL, NA, or character.")
  }

  if (any(include %in% exclude)) {
    stop("You can't include and exclude the same thing.")
  }

  if (!rlang::is_logical(se)) {
    stop("se must be TRUE or FALSE")
  }

  if (!rlang::is_logical(keep_prediction_data)) {
    stop("keep_prediction_data must be TRUE or FALSE")
  }

  # standard prediction would simply call predict.gam
  if (rlang::is_null(re_form) | rlang::is_character(re_form)) {
    if (rlang::is_null(re_form)) {
      preds <- predict(model,
                       newdata,
                       se = se,
                       terms = include,
                       exclude = exclude,
                       ...
      )
    } else {
      preds <- predict(model,
                       newdata,
                       se = se,
                       terms = c(include, re_form),
                       exclude = exclude,
                       ...
      )
    }
  } else if (rlang::is_na(re_form)) {

    # FE only
    re_terms <- sapply(model$smooth, function(x) inherits(x, "random.effect"))
    re_terms <- sapply(model$smooth[re_terms], function(x) x$label)

    preds <- predict(model,
                     newdata,
                     se = se,
                     terms = include,
                     exclude = c(re_terms, exclude),
                     ...
    )
  }

  if (se) {
    preds <- data.frame(prediction = preds$fit, se = preds$se)
  } else {
    preds <- data.frame(prediction = preds)
  }

  if (keep_prediction_data) {
    if (missing(newdata)) {
      base <- model$model
    } else {
      base <- newdata
    }
    preds <- data.frame(base, preds)
  }

  preds
}
```

## COMPUTE DEMING REGRESSION

This section only needed to be run once to compute the fitted values based on the principal axis (Deming regression). The ordinary least squares fitted values were computed in the original data simulation step. The resulting data set is the `eyefitting-model-data.csv` used for analysis.

```{r demming-regression}

# read in feedback and simulated data
eyefitting_feedback_data <- read_csv("https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-feedback-data.csv")
eyefitting_simulated_data <- read_csv("https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-simulated-data.csv")

# fit deming regression
demingFit <- function(data){
  fit <- mcreg(data$x, data$y, method.reg = "Deming")
  demingIntercept <- fit@para[1]
  demingSlope     <- fit@para[2]

  return(tibble(demingIntercept = demingIntercept, demingSlope = demingSlope))
}

pca_preds <- eyefitting_simulated_data %>%
  filter(dataset == "point_data", participant_id %in% unique(eyefitting_feedback_data$participant_id)) %>%
  as_tibble() %>%
  tidyr::nest(-c(participant_id, parm_id)) %>%
  dplyr::mutate(deming_fit = purrr::map(data, demingFit)) %>%
  unnest(deming_fit) %>%
  select(participant_id, parm_id, demingIntercept, demingSlope) %>%
  expand_grid(x = seq(0,20,0.25)) %>%
  mutate(ypca = demingIntercept + demingSlope*x)

eyefitting_model_data <- eyefitting_feedback_data %>%
  left_join(pca_preds, by = c("participant_id", "x", "parm_id")) %>%
  mutate(residual_ols_drawn = ydrawn - yols,
         residual_pca_drawn = ydrawn - ypca) %>%
  dplyr::select(nick_name, study_starttime, age, gender, academic_study, recruitment, participant_id, parm_id, plot_id, x, yols, ypca, ydrawn, residual_ols_drawn, residual_pca_drawn)

# save data to csv - already run once and pushed to GitHub.
# write.csv(eyefitting_model_data, file = "eyefitting-model-data.csv", row.names = F, na = "")
```

@@

De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub at [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-model-data.csv).

```{r data}
eyefitting_model_data  <- read_csv("https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-model-data.csv")

factorCols <- c("nick_name", "study_starttime", "age", "gender", "academic_study",
                "recruitment", "participant_id", "parm_id", "plot_id")
eyefitting_model_data[,factorCols] <- lapply(eyefitting_model_data[,factorCols], factor)
```

There are a total of `length(unique(eyefitting_model_data$participant_id))` participants and `length(unique(eyefitting_model_data$participant_id))` 'You Draw It' plots completed.

```{r data-table, echo = F}
eyefitting_model_data[1:10,] %>%
  kbl() %>%
  kable_paper() %>%
  scroll_box(width = "100%", height = "200px")
```

@@

### EXAMPLE

```{r}
# Example
eyefitting_model_data %>%
  filter(participant_id == "60f510d6896cddc508ea6d3de4b58234", parm_id == "F") %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = yols, color = "OLS", linetype = "OLS")) +
  geom_line(aes(y = ypca, color = "PA", linetype = "PA")) +
  geom_line(aes(y = ydrawn, color = "Drawn", linetype = "Drawn")) +
  geom_point(data = eyefitting_simulated_data %>%
               filter(dataset == "point_data", participant_id == "60f510d6896cddc508ea6d3de4b58234", parm_id == "F"),
             aes(x = x, y = y)) +
  facet_wrap(~ parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_y_continuous("y") +
  scale_color_manual("", values = c("black", "steelblue", "orange2")) +
  scale_linetype_manual("", values = c("dashed", "solid", "solid"))
```

### OLS Spaghetti Plot

```{r y-ols-plot}

eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = ydrawn, group = plot_id), alpha = 0.5, color = "steelblue") +
  geom_line(alpha = 0.2, aes(y = yols, group = participant_id)) +
  facet_wrap(~ parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  ggtitle("OLS")
```

### Principal Axis Spaghetti Plot

```{r y-pca-plot}
eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = ydrawn, group = plot_id), alpha = 0.5, color = "steelblue") +
  geom_line(alpha = 0.2, aes(y = ypca, group = participant_id)) +
  facet_wrap(~ parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  ggtitle("PA")
```

### Residuals Spaghetti Plot

@@

```{r residual-plot}
eyefitting_model_data %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.3) +
  geom_line(aes(y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~parm_id) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 20)) +
  scale_color_manual("Estimate", values = c("steelblue", "orange"))
```

@@

```{r, anova-lmer, echo = F}
sv <- c("participant_id", "parm_id", "x", "x:parm_id", "residual")
df <- c("(50 - 1) = 49", "(4 - 1) = 3", "1", "(4 - 1) = 3", "143 - by subtraction")
data.frame("SV" = sv, "DF" = df) %>% kable()
```

@@

```{r lmer, fig.height = 9}
# OLS
eyefitting.ols.lmer <- lmer(residual_ols_drawn ~ -1 + parm_id + x:parm_id + (1|participant_id),
                       data = eyefitting_model_data)
anova(eyefitting.ols.lmer)

# PCA
eyefitting.pca.lmer <- lmer(residual_pca_drawn ~ -1 + parm_id + x:parm_id + (1|participant_id),
                            data = eyefitting_model_data)
anova(eyefitting.pca.lmer)

@@

# write.csv(eyefitting.preds.lmer, "youdrawit-eyefitting-lmerpred-data.csv", row.names = F, na = "")

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PCA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.pca, color = "PCA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 2) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA"))

@@

```{r gamm, fig.height = 9}
# OLS
eyefitting.ols.gamm <- bam(residual_ols_drawn ~ parm_id + s(x, by = parm_id) + 
                             s(participant_id, bs = "re") +
                             s(x,participant_id, bs = "re"),
            method = "REML",
            data = eyefitting_model_data)

@@

# PCA
eyefitting.pca.gamm <- bam(residual_pca_drawn ~ -1 + parm_id + s(x) +
                             s(x, by = parm_id) +
                             s(participant_id, bs = "re") +
                             s(x,participant_id, bs = "re"),
                           method = "REML",
                           data = eyefitting_model_data)
# evaluate gamm
plot(eyefitting.pca.gamm, pages = 1,all.terms=TRUE)

# Obtain Predictions
eyefitting.grid.gamm <- expand_grid(parm_id = c("S", "V", "F", "N"),
                                    x = seq(0,20, 0.5),
                                    participant_id = eyefitting_model_data$participant_id[1])

@@

# write.csv(eyefitting.grid.gamm, "youdrawit-eyefitting-gammpred-data.csv", row.names = F, na = "")

# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = pca.pred, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 2) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PCA")) 
eyefitting.gamm.plot
```
